\documentclass[11pt,a4paper,sans]{moderncv}  
\moderncvstyle{classic}
\moderncvcolor{purple}

\usepackage[utf8]{inputenc}

\usepackage[scale=0.75]{geometry}

\name{Andrea}{Sánchez Blanco}
\address{1901 Harder Road}{94542, Hayward}{USA}
\phone[mobile]{+1~(323)~891~7585}
\email{contact@asblanco.com}
\homepage{www.asblanco.com}
\quote{Some quote}
\begin{document}
\recipient{Parkside}{Graz}
\date{07 May 2016}
\opening{Dear Christian Moser,}
\closing{Yours faithfully,}
\enclosure[Attached]{Curriculum Vit\ae{}}
\makelettertitle

"Think interactive first". Your slogan makes me think you are doing things the way I also consider to be right. Software Designers are needed to model the product so that it manages to do what it should do, but also in an efficient way, scalable, secure, reusable, maintanable and so on... However, many times UX has been forgotten on this list and I think that's exactly what you are providing to the market.

I am a senior Computer Science student currently located near San Francisco, California, as an exchange student, and I am graduating this summer at University of Vigo, Spain. I am finishing my bachelor's final project, wich is a web application based on Angular 4 and MaterializeCSS in the front-end, and Django/Python as back-end. This means that I enjoy learning state of the art web technologies, as I also did last year in my bachelor's thesis at MAMK, Finland, where I used Ionic 1.0 to develop a small cross-platform application and study the actual benefits of hybrid apps taking into account User Experience.

In addition to this, I have developed some other web applications as university group projects, where in one we won the first possition as best UI design of the class using Bootstrap for responsive front-end and CakePHP as backend. In another one, I was the team leader of 9 members and we developed a web app using Bootstrap/PHP/MySQL, and the last one we used MongoDB/Express /Bootstrap/NodeJS and I was responsible for the look and feel of the web app. As a result of all these projects, I cannot consider myself an expertese in any of them, but I consider that I liked to learn and try new technologies so that I can have now a better perspective of what to use and deep into it more.


For these reasons, I would like my application to be considered for the Javascript Developer position in the beautiful Graz headquartered Parkside.

\makeletterclosing

\end{document}
